Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-18 paper/structureScene.tex
polishing part C exp 1 : remove "centroids"
rename of repo

The implementations of the presented methods and the experimental protocol are available online\footnote{\url{https://github.com/mathieulagrange/paperStructureScene16}}. % \ja{What is ``the one''?}

@@

The different systems are evaluated on the private part of the DCASE 2013 dataset using five-fold stratified cross validation. The folds are identical to those used in the original challenge. The slack parameter $C$ of the SVM is here set to $1$. Both linear and Gaussian RBF kernels are used. For the latter, a local scaling method is applied \cite{selfTuneManor2004}. All feature vectors, that is scattering frames, MFCCs and centroids, are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test splits of the cross validation scheme (see Section \ref{sec:stand}). Optimal scaling parameter $q$ of the RBF kernels is  learned on the public part of the DCASE 2013 dataset, using five-fold stratified cross validation.  For these experiments, both \emph{early} and \emph{late} integration strategies are evaluated (see Section \ref{sec:eili}).

>>>>

The implementations of the presented methods and the experimental protocol are available online\footnote{\url{https://github.com/mathieulagrange/taslp16}}. % \ja{What is ``the one''?}

@@

The different systems are evaluated on the private part of the DCASE 2013 dataset using five-fold stratified cross validation. The folds are identical to those used in the original challenge. The slack parameter $C$ of the SVM is here set to $1$. Both linear and Gaussian RBF kernels are used. For the latter, a local scaling method is applied \cite{selfTuneManor2004}. All feature vectors, that is scattering frames and MFCCs, are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test splits of the cross validation scheme (see Section \ref{sec:stand}). Optimal scaling parameter $q$ of the RBF kernels is  learned on the public part of the DCASE 2013 dataset, using five-fold stratified cross validation.  For these experiments, both \emph{early} and \emph{late} integration strategies are evaluated (see Section \ref{sec:eili}).
